JD notes on effects

### 2022-06-29 manuscript/body.tex
Will JD be available?

\jd{This seems like too much about the other packages. Maybe we could: 1) stake things out a bit better by closing off our overview with the "splash plot" (make that the first figure); 2) write the other-package stuff specifically as a comparison, and make it a bit shorter.}

@@

\caption{{\bf A comparison of min- and center- anchored effects.} The center-anchored effects are based on the mean of the focal predictor while the min-anchored effects are based on the minimum of the focal predictor. As we mentioned earlier, the choice of the anchor do not affect the main estimates (central trend lines). \jd{Can we use zero anchor instead of min?}} 

>>>>

\jd{This seems like too much about the other packages. Maybe we could: 1) stake things out a bit better by closing off our overview with the "splash plot" (make that the first figure); 2) write the other-package stuff specifically as a comparison, and make it a bit shorter.}
\BC{By ``splash plot'' you mean Fig 1? I am suggesting we move all the package comparison stuff to/after statistical background section or maybe to simulation example section ...}

@@

\caption{{\bf A comparison of zero- and center- anchored effects.} The center-anchored effects are based on the mean of the focal predictor while the zero-anchored effects are based on the minimum of the focal predictor. As we mentioned earlier, the choice of the anchor do not affect the main estimates (central trend lines).} 
